---
title: "Regression"
author: "Markos Hay"
date: "12/04/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Motor Trend Car Road Analysis
## Executive Summary

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
“Quantify the MPG difference between automatic and manual transmissions”

## Data Processing

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{R}
library(datasets)
data(mtcars)
```

It consists of 32 observations on 11 variables.

[, 1] mpg Miles/(US) gallon
[, 2] cyl Number of cylinders
[, 3] disp Displacement (cu.in.)
[, 4] hp Gross horsepower
[, 5] drat Rear axle ratio
[, 6] wt Weight (lb/1000)
[, 7] qsec 1/4 mile time
[, 8] vs V/S
[, 9] am Transmission (0 = automatic, 1 = manual)
[,10] gear Number of forward gears
[,11] carb Number of carburetors


## Is an automatic or manual transmission better for MPG?

For Automatic

```{r}
summary(mtcars[mtcars$am==0,])
```

For Manual

```{r}
summary(mtcars[mtcars$am==1,])
```

Hence, the mean of mpg is greater for manual (at 24.4) than automatic (at 17.1).

Investigating further..

## Quantify the MPG difference between automatic and manual transmissions.

```{r}
boxplot(mpg ~ am, data = mtcars, xlab = "Transmission", ylab = "Miles per gallon", main="Miles per gallon by Transmission Type")
```

Manual (represented by 1) has a higher mean for mpg than automatic (represented by 0).

## Hypothesis Testing

```{r}
aggregate(mpg~am, data = mtcars, mean)
```

The mean transmission for manual is 7.24mpg higher than automatic. Let alpha=0.5.

```{r}
auto <- mtcars[mtcars$am == 0,]
manual <- mtcars[mtcars$am == 1,]
t.test(auto$mpg, manual$mpg)
```

Since p-value = 0.001374, we reject the null hypothesis. There is a major difference between mpg of manual and automatic transmissions.

```{r}
m<-lm(mpg~am,data=mtcars)
summary(m)
```

Since p-value = 0.001374, we reject the null hypothesis. There is a major difference between mpg of manual and automatic transmissions.

```{r}
model <- lm(mpg~am + wt + hp + cyl, data = mtcars)
anova(m,model)
```

The final model is below:

```{r}
summary(model)
```

## Concolusion

This model explains 84.9% of the variance. It may be concluded that on average, manual transmissions have 1.478 more mpg than automatic.

# Appendix

```{r}
plot(model)
```

Hence, the residuals are normally distributed, and homoskedastic.